An equivalence of compositional frameworks

### 2019-01-09 EquivCompFrameworks_20180911kc.tex
one more small change - the notation should be consistent now
Alternative way of obtaining double equivalence via pair of double natural isomorphisms?

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item Fix notation for structured and decorated cospans.
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.}
\item Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
\end{itemize}

@@

\textbf{Is this biequivalnce symmetric monoidal? Probably}

We can also define the part of the double equivalence $\mathbb{G} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to _L \mathbb{C} \textnormal{sp}(\mathrm{X})$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathrm{A}}$.

Given a horizontal 1-cell $M$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$x \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\tau_c L(I)$} (B)
(C) edge node[above]{$\tau_ c L(O)$} (B);
\end{tikzpicture}
\]
where $\tau_c \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_c \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$. In other words, the trivial decoraction $!_c$ is initial in $F(c)$ and $\tau_c \colon !_c \to x$ is the unique morphism to $x$. Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$x \in F(c)$};
\node (D') at (1,-1.5) {$x^\prime \in F(c^\prime)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B)
(A') edge node[above]{$I^\prime$} (B')
(C') edge node[above]{$O^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(h)(x) \to x^\prime$$
the image in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1,-1) {$x^\prime$};
\node (C') at (2,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\tau_c L(I)$} (B)
(C) edge node[above]{$\tau_c L(O)$} (B)
(A') edge node[above]{$\tau_{c^\prime} L(I^\prime)$} (B')
(C') edge node[above]{$\tau_{c^\prime} L(O^\prime)$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
where $\alpha \colon x \to x^\prime$ is a morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.

Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathrm{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{\mathbb{F}\textnormal{Cospan}(\mathrm{A})}$. Specifically, these are double natural isomorphisms given by double transformations $\eta$ and $\epsilon$ whose components are isomorphisms.

First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$. On the object categories, both composites are $\id_\mathrm{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathrm{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathrm{A}}$.

Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$:
the horizontal 1-cell $\mathbb{E}(M)$ is given by:
\node (D) at (1,-0.5) {$x \in F(R(x))$};
(A) edge node[above]{$R(i)$} (B)
(C) edge node[above]{$R(o)$} (B);
and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
\node (B) at (1.5,0) {$x$};
\node (C) at (3,0) {$L(c_2)$};
(A) edge node[above]{$\tau_{R(x)}L(R(i))$} (B)
(C) edge node[above]{$\tau_{R(x)}L(R(o))$} (B);
\textbf{What can we say about LR? Find a 2-iso between these in $_L \mathbb{C}\textnormal{sp}(\mathrm{X})$.}
Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathrm{X})$ given by:
\node (B) at (1.25,0) {$x$};
\node (C) at (2.5,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1)$};
\node (B') at (1.25,-1) {$x$};
\node (C') at (2.5,-1) {$L(c_2)$};
(A') edge node[above]{$\tau_{R(x)}L(R(i))$} (B')
(C') edge node[above]{$\tau_{R(x)}L(R(o))$} (B')
(B) edge node [left]{$1$} (B')
On the other hand, given a horizontal 1-cell $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:

@@

(A) edge node[above]{$\tau_c L(I)$} (B)
(C) edge node[above]{$\tau_c L(O)$} (B);

@@

\node (D) at (1,-0.5) {$x \in F(R(x))$};
(A) edge node[above]{$R(\tau_c)I$} (B)
(C) edge node[above]{$R(\tau_c)O$} (B);
Then we can find a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ given by:
\node (D) at (1,0.5) {$x \in F(R(x))$};
\node (D') at (1,-1.5) {$x \in F(c)$};

@@

@@

(A) edge node[above]{$R(\tau_c)I$} (B)
(C) edge node[above]{$R(\tau_c)O$} (B)

@@

@@

Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?}

>>>>

\section*{Various issues-in-progress}
{\chris If Kenny likes, we can use this as a section for all the current issues that need to be resolved, or what we are currently working on or something!}
\begin{itemize}
\item {\chris I think structured cospans should be introduced/recalled way earlier! This is a paper that compares the two,
and both should be presented early.}
\item Sure, I'm fine with that. What section do you think we should bring it up in, or maybe create a new section entirely to mention it?
\end{itemize}

@@

\textbf{Is this biequivalnce symmetric monoidal? Probably}
\newline

We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.

Given a horizontal 1-cell $M$ of $F\mathbb{C}\textnormal{sp}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$x \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the image $\mathbb{G}(M)$ is the horizontal 1-cell in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!_{c} L(I)$} (B)
(C) edge node[above]{$!_{c} L(O)$} (B);
\end{tikzpicture}
\]
where $!_{c} \colon L(c) \to x$ is the unique morphism from the trival decoration on $c$ given by $$!_{c} \coloneqq 1 \xrightarrow{\phi} F(0) \xrightarrow{F(!)} F(c)$$ to $x \in F(c)$. In other words, the trivial decoraction $!_{c}$ is initial in $F(c)$. Similarly, given a 2-morphism $(f,h,g,\iota) \colon M \to M^\prime$ of $F\mathbb{C}\textnormal{sp}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1,0.5) {$x \in F(c)$};
\node (D') at (1,-1.5) {$x^\prime \in F(c^\prime)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (A') at (0,-1) {$c_1^\prime$};
\node (B') at (1,-1) {$c^\prime$};
\node (C') at (2,-1) {$c_2^\prime$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B)
(A') edge node[above]{$I^\prime$} (B')
(C') edge node[above]{$O^\prime$} (B')
(A) edge node [left]{$f$} (A')
(B) edge node [left]{$h$} (B')
(C) edge node [left]{$g$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(h)(x) \to x^\prime$$
the image in $\mathbb{G}(f,h,g,\iota)$ in $_L \mathbb{C}\textnormal{sp}(\mathsf{X})$ is given by the 2-morphism:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1.5,0) {$x$};
\node (C) at (3,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1^\prime)$};
\node (B') at (1.5,-1) {$x^\prime$};
\node (C') at (3,-1) {$L(c_2^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!_{c} L(I)$} (B)
(C) edge node[above]{$!_{c} L(O)$} (B)
(A') edge node[above]{$!_{c^\prime} L(I^\prime)$} (B')
(C') edge node[above]{$!_{c^\prime} L(O^\prime)$} (B')
(A) edge node [left]{$L(f)$} (A')
(B) edge node [left]{$\alpha$} (B')
(C) edge node [left]{$L(g)$} (C');
\end{tikzpicture}
\]
where $\alpha \colon x \to x^\prime$ is the morphism in the Grothendieck construction of $F$ given by $\alpha = (h \colon c \to c^\prime, \iota \colon F(h)(x) \to x^\prime)$.

Next, we exhibit natural isomorphisms $\eta \colon \id_{ _L \mathbb{C}\textnormal{sp}(\mathsf{X})} \cong \mathbb{G} \mathbb{E}$ and $\epsilon \colon \mathbb{E} \mathbb{G} \cong \id_{F\mathbb{C}\textnormal{sp}}$. Specifically, these are double natural isomorphisms given by double transformations \cite{Shul2} $\eta$ and $\epsilon$ whose object and arrow components are isomorphisms.

First we compute the composites $\mathbb{G} \mathbb{E}$ and $\mathbb{E} \mathbb{G}$. On the object categories, both composites are $\id_\mathsf{A}$ and we have natural isomorphisms $\eta \colon \id_{\mathsf{A}} \cong \mathbb{G}_0 \mathbb{E}_0$ and $\epsilon \colon \mathbb{E}_0 \mathbb{G}_0 \cong \id_{\mathsf{A}}$.

Given a horizontal 1-cell $M$ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(x)$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$x \in F(R(x))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(i) \eta_{c_1}$} (B)
(C) edge node[above]{$R(o) \eta_{c_2}$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{G} \mathbb{E}(M)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1.5,0) {$x$};
\node (C) at (3,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B)
(C) edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B);
\end{tikzpicture}
\]
Then we can find a 2-isomorphism $\eta_M \colon M \xrightarrow{\sim} \mathbb{G}\mathbb{E}(M) $ in $_L \mathbb{C} \textnormal{sp}(\mathsf{X})$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1.5,0) {$x$};
\node (C) at (3,0) {$L(c_2)$};
\node (A') at (0,-1) {$L(c_1)$};
\node (B') at (1.5,-1) {$x$};
\node (C') at (3,-1) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A') edge node[above]{$!_{R(x)}L(R(i)\eta_{c_1})$} (B')
(C') edge node[above]{$!_{R(x)}L(R(o)\eta_{c_2})$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$1$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
where
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (-0.5,0) {$L(c_1)$};
\node (B) at (1,0) {$L(R(L(c_1)))$};
\node (C) at (2.5,0) {$L(R(x))$};
\node (D) at (3.5,0) {$x$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$L(\eta_{c_1})$} (B)
(B) edge node[above]{$L(R(i))$} (C)
(C) edge node[above]{$!_{R(x)}$} (D)
(A) edge[bend right] node [above]{$i$} (D);
\end{tikzpicture}
\]
commutes.

On the other hand, given a horizontal 1-cell $N$ in $F\mathbb{C}\textnormal{sp}$:

@@

(A) edge node[above]{$!_c L(I)$} (B)
(C) edge node[above]{$!_c L(O)$} (B);

@@

\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};
\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
Then we have a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
\node (D) at (1.5,0.5) {$x \in F(R(x))$};
\node (D') at (1.5,-1.5) {$x \in F(c)$};

@@

\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};

@@

\node (B') at (1.5,-1) {$c$};
\node (C') at (3,-1) {$c_2$};
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)

@@

\node (B) at (1,0) {$R(L(c_1))$};
\node (C) at (2.5,0) {$R(L(c))$};
\node (D) at (3.5,0) {$R(x)$};
\node (E) at (4.5,0) {$c$};
(A) edge node[above]{$\eta_{c_1}$} (B)
(B) edge node[above]{$R(L(I))$} (C)
(C) edge node[above]{$R(!_c)$} (D)
(D) edge node[above]{$e$} (E)
(A) edge[bend right] node [above]{$I$} (E);
commutes.

@@

Daniel Cicala, person that Christina emailed about lax slice category? {\chris did you use it after all?} No, I did not.
